---
title: "'letiRmisc': miscellaneous functions of the letiRmisc group"
output:
    md_document
---


```{r setup, echo=FALSE, message = FALSE}
knitr::opts_chunk$set(
  fig.path = "inst/assets/fig/",
  comment = "R>> ",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 5,
  fig.height = 5
)
```


# inSilecoMisc

[![Build Status](https://travis-ci.org/inSileco/inSilecoMisc.svg?branch=master)](https://travis-ci.org/inSileco/inSilecoMisc)
[![Build status](https://ci.appveyor.com/api/projects/status/rskiyadk6urmsrox/branch/master?svg=true)](https://ci.appveyor.com/project/KevCaz/insilecomisc/branch/master)
[![codecov](https://codecov.io/gh/inSileco/inSilecoMisc/branch/master/graph/badge.svg)](https://codecov.io/gh/inSileco/inSilecoMisc)

## About

### Description

The *inSilecoMisc* package is a set of useful R functions created to ease some
operations we often do.
Functions here are written to be used with base may already be available in other
packages (especially in packages of the [tidyverse](https://www.tidyverse.org/)).

So far, we do not intend to release this package on the CRAN. If you however
find one of these function and intend to use it in your own package, please,
help yourself!

Note that functions' names are written using Camel case (*e.g.* `keepWords()`).



## Installation

To get the current development version from Github, use the
[*devtools*](http://cran.r-project.org/web/packages/devtools/index.html) package
like so:

```{r eval=FALSE}
if (!require("devtools")) install.packages("devtools")
devtools::install_github("inSileco/inSilecoMisc")
```





## Tout-doux list

- [ ] inSilecico member, a short but useful function you often use? Add it in this repo :stuck_out_tongue_winking_eye:;
