---
title: "inSilecoMisc, an overview"
author: "inSileco group"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{An overview of letiRmisc package}
  %\VignetteEngine{knitr::rmarkdown}
---


```{r echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "R> ",
  collapse = TRUE
)
library(inSilecoMisc)
```

This vignette is a short overview of *inSilecoMisc* organized around the following themes:

1. strings manipulations
2. vector manipulations
3. data frames manipulations
4. Mathematical functions


# String manipulations

## LoremIpsum

It is sometime useful to have a piece of random text to play with,
`loremIpsum()` display a piece of the commonly used placeholder text
[Lorem ipsum](https://en.wikipedia.org/wiki/Lorem_ipsum) with the option of
having a specific number of words.

```{r loremIpsum}
loremIpsum()
loremIpsum(10)
```

## Keep a selection of words or letters

```{r keepWords}
lor <- loremIpsum()
keepWords(lor, c(1,4))
vlor <- lapply(c(2, 3), loremIpsum)
vlor
keepLetters(vlor, c(1:2, 15))
```



## Adjust the size of a character string

```{r adjustString}
paste0('myfilename', adjustString(c(1:2, 10, 100), 3))
```

## Assign a symbol to a p-value

```{r signifSymbols}
sapply(c(.2, .08, .04, .008, 0.0001), signifSymbols)
```

## Add URL and icons

```{r addURL}
addURL("https://github.com/inSileco/letiRmisc", "Github repo")
addURL("https://github.com/inSileco/letiRmisc", "Github repo", markdown=TRUE)
```

```{r addWebIcon}
addWebIcon('cc')
addWebIcon('acm', 'ai', 4)
```

## applyString

```{r stApply}
applyString("cool", FUN = toupper, pos = 1:2)
applyString(c("cool", "pro"), pattern = "o", FUN = toupper)
```

## Extract digits from strings

```{r getDigits}
getDigits(c("a1", "032hdje2832"))
```




# Vectors manipulations


## whichIs

```{r whichIs}
vec <- LETTERS[1:7]
spl <- sample(vec)
whichIs(vec, spl)
id <- unlist(whichIs(vec, spl))
spl[id]
```

## meanAlong

```{r meanAlong}
meanAlong(1:10, 2)
```

## scaleWithin

```{r scaleWithin}
val <- runif(1000, 0, 100)
res1 <- scaleWithin(val, 20, 40, 60)
```







# Data frame manipulation


## Assign a category

```{r categorize}
(seqv <- stats::runif(40))
categorize(seqv, categ=seq(0.1,0.9, 0.1))
```


## Turn a matrix or a data frame into a squared matrix

```{r squaretize}
mat <- matrix(1:15, 3, 5, dimnames = list(LETTERS[3:1], LETTERS[1:5]))
print(mat)
squaretize(mat, reorder = FALSE)
```


## Assign classes to data frames' columns

```{r setColClass}
df1 <- matrix(signif(runif(20),4), ncol = 2)
df2 <- setColClass(df1, 2, 'character')
str(df1)
str(df2)
```

## Create data frame from scratch or from other data frame

```{r dfTemplate}
dfA <- data.frame(col1 = c(1, 2), col2 = LETTERS[1:2])
dfB <- data.frame(col1 = 2, col4 = "cool")

dfTemplate(2, 2)
dfTemplate(2, 2, fill = 0)
dfTemplate(c("value", "name"), 2, col_classes = c("numeric", "character"))

dfTemplateMatch(dfA, c("col4"))
dfTemplateMatch(dfA, dfB)
dfTemplateMatch(dfA, c("col1", "col4"), yonly = TRUE)
dfTemplateMatch(dfA, c("col1", "col2"), yonly = TRUE, col_classes = "numeric", fill = 0)
```

## packagesUsed

```{r packagesUse}
packagesUsed(c('utils', 'methods'))
```




# Mathematical functions

## Logistic functions

```{r logistic}
seqx <- seq(-5, 5, 0.1)
par(mfrow = c(1, 2))
plot(seqx, logistic(seqx))
plot(seqx, logistic2(seqx))
```
